Foregrounds in Fourier Space for Redshifted 21~cm Observatories

### 2015-02-06 ms.tex
Move delay deconvolution to delay spectrum section
from c25e8ca:
============

In ms.tex,

(*) Move Delay spectrum deconvolution section to end of Delay Spectrum
section and simplify text to be more general

@@

\subsection{Deconvolved Delay Spectrum}\label{sec:data-delay-spectrum}

We obtain the delay spectrum of these calibrated visibilities by taking the delay transform of each baseline's spectrum (equation~\ref{eqn:delay-transform}) choosing $W'_f$ to be a {\it Blackman--Harris} window function. The spectrum is multiplied by the additional weight of the flagged channels which occur rarely for interference and regularly every 1.28~MHz where the edges of coarse channels are known to have a small aliasing effect. In delay--space, these weights translate into a convolution by a grated point spread function (PSF) with gratings at multiples of $\tau=0.78\,\mu$s. We deconvolve this PSF using a one dimensional CLEAN algorithm \citep{tay99} as described for the delay axis by \citet{par09,par12b}. The CLEAN procedure iteratively finds and subtracts peak values convolved by the Fourier transform of the weights. We limit the selection of peaks to modes inside the horizon delay limit, corresponding to smooth spectrum objects in the visible sky hemisphere.

% In subsequent sections, we plot the amplitude of the delay spectrum, $|V_{b\tau}|$, sorted by baseline length, $|\boldsymbol{b}|$. Note that visibilities from different baselines have not been averaged together in this analysis.

% Figure~\ref{fig:fhd_data} shows {\bf delay power spectra} from MWA data after deconvolution along the delay axis. The principal feature is the {\it foreground wedge}, whose boundaries, marked by white lines, increase linearly with light travel time proportional to baseline length. Note that the wedge is not filled out uniformly. Each baseline has a different orientation that determines the response to different objects in the sky. It is this variation that we will explore below.

The {\it off--zenith} pointing {\bf has notably higher power in the {\it foreground wedge} than in the {\it zenith} pointing}. This is shown later in \S\ref{sec:diffuse} to be due to response of the array to the bright Galactic center and Galactic plane in the westward sky. Consequently, the contamination into the {\it EoR window} is also higher, especially on short antenna spacings. Emission in the {\it zenith} pointing is more centrally concentrated {\bf due to a zenith--centered power pattern and faster suppression of response away from zenith}, whereas the {\it off--zenith} pointing has a power pattern phased eastward of zenith and is also more responsive to emission farther away from the primary lobe relative to that in the {\it zenith} pointing. {\bf The power pattern is discussed in detail in \S\ref{sec:instrument_model}}.

% \begin{figure}[htb]
% \centering
% % \includegraphics[width=\linewidth]{figures/v1_0/multi_baseline_fhd_delay_spectrum_snapshots.eps}
% % \includegraphics[width=\linewidth]{f3.eps}
% \includegraphics[width=\linewidth]{fig4.eps}
% \caption{{\bf Delay power spectra} of two observations of the EoR field (RA = 0$^\textrm{h}$, Dec = $-30\arcdeg$) at an {\it off--zenith} pointing (top) when tiles have significant secondary lobes in the direction of the Galactic center and a {\it zenith} pointing (bottom) where secondary lobes are minimal and the Galaxy has set. {\bf In both cases, the delay spectra are phased to the zenith and thus the {\it foreground wedge} boundaries are symmetric around $\tau=0$}. For reference, the $k$--space equivalent of $\tau$ and $|\boldsymbol{b}|$, namely, $k_\parallel$ and $k_\perp$ are shown at the axes on the right and top respectively. White lines mark the boundaries of {\it foreground wedge} determined by light travel time across each baseline. Smooth spectrum objects predominantly reside in this {\it foreground wedge}. The logarithmic color scale (shown at the right) is common to both panels. \label{fig:fhd_data}}
% \end{figure}

>>>>

\subsection{Delay Spectrum Deconvolution}\label{sec:data-delay-spectrum}

We obtain the delay spectrum of visibilities by taking the delay transform of each baseline's spectrum (equation~\ref{eqn:delay-transform}) choosing $W'_f$ to be a {\it Blackman--Harris} window function. The spectrum is multiplied by the additional weights, $W_f$, consisting of instrumental passband and channels possibly flagged for interference. In delay--space, these weights translate into a convolution by a point spread function (PSF). We deconvolve this PSF using a one dimensional CLEAN algorithm \citep{tay99} as described for the delay axis \citep{par09,par12b} to obtain the final delay spectra. The CLEAN procedure iteratively finds and subtracts peak values convolved by the Fourier transform of the weights. We limit the selection of peaks to modes inside the horizon delay limit, corresponding to smooth spectrum objects in the visible sky hemisphere.

@@
